```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r load-libraries}
library(tidyverse)
library(caret)
library(glmnet)
library(tidymodels)
library(MLmetrics)
library(Metrics)
```

```{r load-data-stores}
stores_all <- read_csv("data//raw_data//stores_all.csv")
```

# get only shufersal stores
```{r select-shufersal-subchains}

shufersal_stores = stores_all[stores_all$ChainName == "שופרסל",]
```

# get chains: shely, deal and express
```{r get-spesific-chains}

shufersal_stores = shufersal_stores[shufersal_stores$SubChainId ==1 | 
                                      shufersal_stores$SubChainId ==2 | 
                                      shufersal_stores$SubChainId == 7,]
```

# assign area to each record
```{r create-area}

shufersal_stores <- shufersal_stores[,] %>% mutate(area = "")

for(i in 1:nrow(shufersal_stores))
{
  city = shufersal_stores[i,"City"]
  north = c("כרמיאל","טבריה","קצרין","קרית שמונה","חיפה")
  center = c("תל אביב","תל-אביב","תל אביב-יפו","חולון","רמת גן","פתח-תקוה"
             ,"ראשון לציון")
  south = c("אשדוד","באר שבע","אשקלון","דימונה","אילת")
  if (city %in% north)
  {
    shufersal_stores[i,"area"] = "north"
  }
  else
  {
    if(city %in% center)
    {
      shufersal_stores[i,"area"] = "center"
    }
    else
    {
      if (city %in% south)
      {
        shufersal_stores[i,"area"] = "south"
      }
      else
      {
        shufersal_stores[i,"area"] = "other"
      }
    }
  }
}
```

# work only with the columns we need
```{r subset-columns-stores}

shufersal_stores= shufersal_stores[,c("SubChainId","StoreId","area")]
```

# assign numeric value to most 3 sub chain with the highest count of stores
```{r assign-subchain-id}

for(i in 1:nrow(shufersal_stores))
{
  id = shufersal_stores[i,"SubChainId"]
  if (id == 1)
  {
    shufersal_stores[i,"SubChainId"] = 1 # shely
  }
  else
  {
    if(id == 2)
    {
      shufersal_stores[i,"SubChainId"] = 2 # deal
    }
    else
    {
      if (id == 7 )
      {
        shufersal_stores[i,"SubChainId"] = 3 # express
      }
      else
      {
         shufersal_stores[i,"SubChainId"] = 0 
      }
    }
  }
}
```

# remove stores that are with other area or 0 chain id
```{r drop-other-area}

shufersal_stores <- shufersal_stores[shufersal_stores$area != "other",]
shufersal_stores <- shufersal_stores[shufersal_stores$SubChainId != 0,]

```

```{r load-data-shufersal}

shufersal_prices <- read_csv("data//raw_data//shufersalPrices.csv")

```

# work only with the columns we need
```{r subset-cols-prices}

shufersal_prices = shufersal_prices[,c("store_id","PriceUpdateDate","ItemCode","ItemPrice")]
```

# join the items df with the stores df 
```{r join-prices-stores}

df_items_stores = merge(x=shufersal_prices ,y=shufersal_stores, by.x = "store_id", by.y = "StoreId")
```

# work only with the columns we need
```{r subset-cols-after-join}

df_items_stores = df_items_stores[,c("PriceUpdateDate","ItemCode","ItemPrice","area","SubChainId")]
```

# convert numeric values to the chain(string)
```{r convert-subchainid-char}

df_items_stores <- df_items_stores %>% 
  mutate(SubChainId= case_when(
    SubChainId == 1 ~ "shely",
    SubChainId == 2 ~ "deal",
    SubChainId == 3 ~ "express"))
```


```{r items-stores-groupby}

df_items_stores = df_items_stores %>% 
  group_by(ItemCode,area,SubChainId,PriceUpdateDate) %>%
  filter(n() > 1)
```


# calculate the price delta
```{r groupby-price-delta}

df_items_stores = df_items_stores %>% group_by(ItemCode,area,SubChainId) %>%
    slice(which.max(PriceUpdateDate),
          which.min(PriceUpdateDate)) %>% 
            dplyr::summarise(last_price=first(ItemPrice),
                      last_update=first(PriceUpdateDate), 
              first_price = last(ItemPrice),      
              first_update=last(PriceUpdateDate))

```

```{r calc-price-delta}

df_items_stores$price_delta <- 
  df_items_stores$last_price - df_items_stores$first_price
```

# create dummy variables -> Prevent "Dummy Variables Trap" 
```{r create-dummy-vars}

df_items_stores$area_south = ifelse(df_items_stores$area == "south",1,0)

#df_items_stores$area_center = ifelse(df_items_stores$area == "center",1,0)
df_items_stores$area_north = ifelse(df_items_stores$area == "north",1,0)

df_items_stores$chain_shely = ifelse(df_items_stores$SubChainId == "shely",1,0)

df_items_stores$chain_deal = ifelse(df_items_stores$SubChainId == "deal",1,0)

```

```{r subset-cols-after-dummy}

df_items_stores = df_items_stores %>%
  select(-c("first_price","area","SubChainId","last_update","first_update"))
```

# get min max for the normalization 
```{r itemcode-min-max}

original_code_min = min(df_items_stores$ItemCode)

original_code_max = max(df_items_stores$ItemCode)
```

# normalize item code
```{r normalize-item-code}

df_items_stores <- df_items_stores %>%
  mutate(item_code_norm = 
           ((ItemCode-original_code_min)/(original_code_max-original_code_min)))
```

```{r pricedelta-min-max}

original_delta_min = min(df_items_stores$price_delta)

original_delta_max = max(df_items_stores$price_delta)
```

```{r normalize-price-delta}

df_items_stores = df_items_stores %>%
  mutate(delta_norm = 
           ((price_delta-original_delta_min)/(original_delta_max-original_delta_min)))
```

# remove non relevnt column
```{r subset-not-norm-itemcode}

df_items_stores = df_items_stores %>% select(-ItemCode)
```


# split to train and test
```{r train-test-split}

set.seed(222)

index=sample(2,nrow(df_items_stores), replace = TRUE, prob = c(0.7,0.3))

train_data = df_items_stores[index == 1,]

test_data = df_items_stores[index == 2,]
```


# build multi linear regression model
```{r multi-lm-model}

model <- lm(
   last_price ~ price_delta  + area_south + area_north + chain_deal + chain_shely,
   data = train_data)

summary(model)
```

```{r model-coef}

summary(model)$coef
```


```{r model-stats}

predictions = predict(model,test_data)

rmse = RMSE(predictions,test_data$last_price)

mse = mse(predictions,test_data$last_price) ################# ERROR

r2 = R2(predictions,test_data$last_price)
```


```{r normalize-rmse}

max_price = max(train_data$last_price)  

min_price = min(train_data$last_price)  

rmse_normalized = rmse/(max_price-min_price)

rmse_normalized  # 0.02641027
```

```{r count-price-delta-train}

cnt_positive = train_data[train_data$price_delta > 0,]

cnt_negative = train_data[train_data$price_delta < 0,]

cnt_zero = train_data[train_data$price_delta == 0,]
```

```{r model-anova}

anova(model)
```

```{r model-plot}

plot(model)
```

